Note about WSC

### 2015-03-13 notes.tex
standard deviation for exp C & power law curves for each exp

\subsection{Comparison}
In order to compare the different mechanisms used in the different paper we will cross them  following the table \ref{tab:exp}.
\begin{table}
	\centering
	\begin{tabular}{l|c|c}
		& Eco\footnote{a} & Rand \\\hline
		$\mu$ &A & B \\
		$\mu +\alpha$ & B & C \\
	\end{tabular}
	\caption{Experimental Setup}
	\label{tab:exp}
\end{table}

>>>>

\subsection{Comparison}
In order to compare the different mechanisms used in the different paper we will cross them  following the table \ref{tab:exp}.
\begin{table}
	\centering
	\begin{tabular}{l|c|c}
		& Rand & Gintis \\\hline
		$\mu$ &A & B \\
		$\mu +\alpha$ & C & D \\
	\end{tabular}
	\caption{Experimental Setup}
	\label{tab:exp}
\end{table}

First we check how those different mechanisms impact the power law distribution.

\begin{figure}[hbp]
	\begin{center}
		\includegraphics[width=6cm]{img/powerABCD.png}
	\end{center}
	\caption{power law for each exp define in table \ref{tab:exp} after 2000 step}
	\label{fig:powerABCD}
\end{figure}

As expected depending on the selection process the repartition follow a power law (random selection) or a exponential law).

Next let's have a look which combination lead to the right economical processes.

\begin{table}
	\centering
	\begin{tabular}{l c c}
		& Random Transmission & Gintis Transmission \\
		FRI & \raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP2.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP2.png}} \\
		GRI & \raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP3.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP4.png}}

	\end{tabular}
	\caption{Evolution of SD. FRI : Fully Random Innovation, GRI: Gintis Random Innovation}
	\label{tab:sdevol}
\end{table}
